\section{agenda}
	The agenda was passed, with the following additions:

	\begin{enumerate}
		\item What graphic design resources are we going to need?
		\item When do we want to have the Zine together by?
		\item Events
	\end{enumerate}

	Which we placed at the beginning of the Agenda.
\section{Graphic Design Resources}
	\subsection{Wordpress}
		it turns out nobody present knows much of anything about the wordpress. As such, we weren't able to generate any data.
	\subsection{Mastodon\&Matrix}
	Things like custom emojis, icons, backgrounds, colour schemes.

	For know, it looks like @GoodnightGirl will be leading this project.

	At some point we might switch to more Adbusters-y, avant-garde typesetting, but for now we really should automate it.
\section{Positions}
	We wont have formal Buddies for this first edition, but we hope to buddy up most positions by the second edition.

	Visual Art Director: Emberlynn (@GoodnightGirl)

	General Editor: Kyle (@KyleN)

	Everything Else: jacob (@aljedaxi) \& kinda Val (@soundsofearth)
\section{Zine Timeline/Release Schedule}
	Have July Edition, to release on July First.

	Three weeks for a call to submission; 

	one week to put everything together, and collect late submissions

	one week to print, bind, disseminate, and come up with/vote on a theme for next zine.
\section{Theme[s]}
	\begin{enumerate}
		\item Introduction to Permeate
		\item Home
		\item psycho-geography (lets do this second)
		\item the permeate guide to: the future
		\item the permeate guide to: the present
		\item the permeate guide to: the past
		\begin{enumerate}
			\item One cover will say The Permeate Guide to: the Future, and the other will say

			The Permeate Guide to: the Past; each one will slowly wind into the center, the present.
		\end{enumerate}
		\item the permeate guide to: pro-social activity
		\item Milkshakes (and how they bring all the boys to the community garden) (how do we get chads to do manual labour for us?)

		\item tech \& primitivism
		\item how to (edition, or a section?)
		\item the permeate guide to: the self and identity
		\item in this edition, we tell you how to think
		\item the permeate guide to: bonding with your friends and family
		\item gender and earth
		\item Ram Ranch (something to do with alberta, sex, sexuality?)
		\item Swords (and Plowshares (and Shovels (and Hoes (and Wheelbarrows (and how one relates to objects)))))
		\begin{enumerate}
			\item The permeate Guide to making love to your sword
			\item Don't do that! Swords will fucking cut you wide open!
		\end{enumerate}
		\item Gotta Bulk up for the Big Community Garden
		\item 10 Crazy Plant Facts! 20 Crazy Plant Life Hacks For All You Plant Lovers! 100 Juiced Up Plants and 100 Juiced Up Fungi!
		\item Visions of Eco Utopias
	\end{enumerate}
	Whenever anyone has an idea, be sure to send it to the chat. 
\section{Aesthetic[s]}
	Serif fonts
\section{Launch Parties}
	Launch parties for the Zine, including readings, maybe some music.

	Sigla deez nutz?

\section{,,with that, i am officially adjourning the meeting``}
